Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Default time span
min.year <- 1488
max.year <- 1828

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  #p <- p + facet_grid(. ~ catalog)		  
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

### Fig 4: Average title length (word count)

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
# Analysis time window
df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
              group_by(catalog, publication_decade) %>%
              summarize(mean_title_length = mean(title_length_wordcount),
	      		n = n())

  p <- ggplot(df, aes(x = publication_decade, y = mean_title_length, fill = catalog)) +
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #geom_point(aes(size = n), size = 5) +
       #geom_line(size = 1) +
       scale_fill_manual(values = c("darkgray", "black")) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE)) +       
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle(paste("Mean title length (", catal, ")", sep = ""))

  print(p)

@@

### Fig. 7A: Publishing activity and riksdagar: Kungliga

```{r Fig7A, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

@@

### Fig. 7B: Publishing activity and riksdagar: Fennica

```{r Fig7B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
minyear <- 1760
maxyear <- 1860
catal <- "Fennica"

df00 <- df.full %>% filter(publication_year >= minyear & publication_year <= maxyear)

  # Use timeinterval year intervals
  dfsel <- subset(df00, catalog == catal)

  df <- df00
  df <- subset(df, catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)

  df$unity <- rep(1, nrow(df))
  publications <- tapply(df$unity, list(df$timeunit), sum)

  publications[is.na(publications)] <- 0 # Set NAs to 0
  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
  dfm <- melt(publications) 
  names(dfm) <- c("Time", "Documents")
  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
  ymin <- min(dfm$Documents)
  ymax <- max(dfm$Documents)

               max(na.omit(dfm$date)))

  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    ymin = ymin,
    ymax = ymax
    )

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         scale_fill_brewer(palette="Greys") +
	 guides(fill = "none")

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
  p <- p + xlim(c(minyear, maxyear))
  print(p)
```

>>>>

```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

### Fig 4: Median title length (word count)

Loess smoothing.

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=14, fig.width=7}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

pics <- list()
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal), aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (word count)")
}

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```

@@

### Fig. 7: Publishing activity and riksdagar: Kungliga

```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

@@
